SSwAB-IT Phase 1 Analysis

### 2025-02-28 Jordana Hoppe/SSwAB-IT/phase_1_analysis.qmd
B&W Euler diagrams

```{r}
agreement <- function(bug, data = df) {
  cos <- paste0(bug, "_cos")
  sos <- paste0(bug, "_sos")
  d <- data[, c(cos, sos)]
  colnames(d) <- c("COS", "SOS")
  d <- d[complete.cases(d), ]
  # Agreement metrics
  c <- confusionMatrix(d$SOS,
    reference = d$COS,
    positive = "Positive", mode = "everything",
    dnn = c("SOS", "COS")
  )
  # Print
  cat("\n")
  cat("\n")
  cat("####", "2x2 Table")
  cat("\n")
  cat("\n")
  d %>%
    tbl_cross(percent = "cell") %>%
    print()
  cat("\n")
  cat("\n")
  cat("####", "2x2 Table (With CIs)")
  cat("\n")
  cat("\n")
  d %>%
    tbl_summary(by = COS, percent = "cell") %>%
    add_ci(method = list(all_categorical() ~ "wald")) %>%
    print()
  cat("\n")
  cat("\n")
  cat("Overall accuracy (both negative/negative and positive/positive) was ",
    scales::percent(c$overall["Accuracy"], accuracy = 0.1), " (95% CI: ",
    scales::percent(c$overall["AccuracyLower"], accuracy = 0.1), " - ",
    scales::percent(c$overall["AccuracyUpper"], accuracy = 0.1), ").",
    sep = ""
  )
  cat("\n")
  cat("\n")
  cat("Kappa was ", round(c$overall["Kappa"], 3), ".", sep = "")
  cat("\n")
  cat("\n")
  cat("#### Euler diagram of negative results")
  cat("\n")
  cat("\n")
  print(plot(euler(d == "Negative"),
    quantities = list(cex = 3),
    fills = list(fill = c("#FFC107", "#1E88E5", "#004D40"))
  ))
  cat("\n")
  cat("\n")
  cat("#### Euler diagram of positive results")
  cat("\n")
  cat("\n")
  print(plot(euler(d == "Positive"),
    quantities = list(cex = 3),
    fills = list(fill = c("#FFC107", "#1E88E5", "#004D40"))
  ))
  cat("\n")
  cat("\n")
}
agreement_test <- function(bug, group = "group", data = df) {
  # Prepare data
  cos <- paste0(bug, "_cos")
  sos <- paste0(bug, "_sos")
  d <- data[, c(cos, sos, group)]
  d <- d[complete.cases(d), ]
  colnames(d) <- c("COS", "SOS", "Group")
  # Agreement and detailed agreement
  d$agree <- d$COS == d$SOS
  d$detailed_agree <- paste0("COS ", d$COS, "/", "SOS ", d$SOS)
  d$detailed_agree <- factor(d$detailed_agree,
    levels = c(
      "COS Negative/SOS Negative", "COS Negative/SOS Positive",
      "COS Positive/SOS Negative", "COS Positive/SOS Positive"
    ),
    labels = c("COS-/SOS-", "COS-/SOS+", "COS+/SOS-", "COS+/SOS+")
  )
  # Print
  cat("\n")
  cat("\n")
  d %>%
    select(agree, detailed_agree, Group) %>%
    tbl_summary(by = Group, missing_text = "Missing", label = list(
      agree ~ "Agree (+/+ and -/-)",
      detailed_agree ~ "Detailed Agreement"
    )) %>%
    add_overall() %>%
    add_p(test.args = all_tests("fisher.test") ~ list(workspace = 2e9)) %>%
    separate_p_footnotes() %>%
    modify_footnote(everything() ~ NA) %>%
    print()
  cat("\n")
  cat("\n")
}
```

@@

>>>>

```{r}
agreement <- function(bug, data = df) {
  cos <- paste0(bug, "_cos")
  sos <- paste0(bug, "_sos")
  d <- data[, c(cos, sos)]
  colnames(d) <- c("COS", "SOS")
  d <- d[complete.cases(d), ]
  # Agreement metrics
  c <- confusionMatrix(d$SOS,
    reference = d$COS,
    positive = "Positive", mode = "everything",
    dnn = c("SOS", "COS")
  )
  # Print
  cat("\n")
  cat("\n")
  cat("####", "2x2 Table")
  cat("\n")
  cat("\n")
  d %>%
    tbl_cross(percent = "cell") %>%
    print()
  cat("\n")
  cat("\n")
  cat("####", "2x2 Table (With CIs)")
  cat("\n")
  cat("\n")
  d %>%
    tbl_summary(by = COS, percent = "cell") %>%
    add_ci(method = list(all_categorical() ~ "wald")) %>%
    print()
  cat("\n")
  cat("\n")
  cat("Overall accuracy (both negative/negative and positive/positive) was ",
    scales::percent(c$overall["Accuracy"], accuracy = 0.1), " (95% CI: ",
    scales::percent(c$overall["AccuracyLower"], accuracy = 0.1), " - ",
    scales::percent(c$overall["AccuracyUpper"], accuracy = 0.1), ").",
    sep = ""
  )
  cat("\n")
  cat("\n")
  cat("Kappa was ", round(c$overall["Kappa"], 3), ".", sep = "")
  cat("\n")
  cat("\n")
  cat("#### Euler diagram of negative results")
  cat("\n")
  cat("\n")
  print(plot(euler(d == "Negative"), quantities = list(cex = 3)))
  cat("\n")
  cat("\n")
  cat("#### Euler diagram of positive results")
  cat("\n")
  cat("\n")
  print(plot(euler(d == "Positive"), quantities = list(cex = 3)))
  cat("\n")
  cat("\n")
}
agreement_test <- function(bug, group = "group", data = df) {
  # Prepare data
  cos <- paste0(bug, "_cos")
  sos <- paste0(bug, "_sos")
  d <- data[, c(cos, sos, group)]
  d <- d[complete.cases(d), ]
  colnames(d) <- c("COS", "SOS", "Group")
  # Agreement and detailed agreement
  d$agree <- d$COS == d$SOS
  d$detailed_agree <- paste0("COS ", d$COS, "/", "SOS ", d$SOS)
  d$detailed_agree <- factor(d$detailed_agree,
    levels = c(
      "COS Negative/SOS Negative", "COS Negative/SOS Positive",
      "COS Positive/SOS Negative", "COS Positive/SOS Positive"
    ),
    labels = c("COS-/SOS-", "COS-/SOS+", "COS+/SOS-", "COS+/SOS+")
  )
  # Print
  cat("\n")
  cat("\n")
  d %>%
    select(agree, detailed_agree, Group) %>%
    tbl_summary(by = Group, missing_text = "Missing", label = list(
      agree ~ "Agree (+/+ and -/-)",
      detailed_agree ~ "Detailed Agreement"
    )) %>%
    add_overall() %>%
    add_p(test.args = all_tests("fisher.test") ~ list(workspace = 2e9)) %>%
    separate_p_footnotes() %>%
    modify_footnote(everything() ~ NA) %>%
    print()
  cat("\n")
  cat("\n")
}
```

@@

# Manuscript Figures

```{r}
# All pathogens
d_overall <- df[, c("overall_cos", "overall_sos")]
colnames(d_overall) <- c("COS", "SOS")
d_overall <- d_overall[complete.cases(d_overall), ]
a1 <- plot(euler(d_overall == "Positive"), quantities = list(cex = 3))
a2 <-
  ggplot(as.data.frame(table(d_overall$COS, d_overall$SOS)), aes(Var1, Var2)) +
  geom_tile(color = "white", fill = "#1E88E5") +
  geom_text(
    aes(label = paste0(Freq, "\n(", round(Freq / sum(Freq), 3) * 100, "%)")),
    color = "white"
  ) +
  xlab("COS") +
  ylab("SOS") +
  theme_bw() +
  theme(text = element_text(size = 15))
# MRSA
d_MSSA <- df[, c("staphylococcus_aureus_cos", "staphylococcus_aureus_sos")]
colnames(d_MSSA) <- c("COS", "SOS")
d_MSSA <- d_MSSA[complete.cases(d_MSSA), ]
b1 <- plot(euler(d_MSSA == "Positive"), quantities = list(cex = 3))
b2 <-
  ggplot(as.data.frame(table(d_MSSA$COS, d_MSSA$SOS)), aes(Var1, Var2)) +
  geom_tile(color = "white", fill = "#1E88E5") +
  geom_text(aes(label = paste0(Freq, "\n(", round(Freq / sum(Freq), 3) * 100, "%)")),
    color = "white"
  ) +
  xlab("COS") +
  ylab("SOS") +
  theme_bw() +
  theme(text = element_text(size = 15))
p1 <- ggarrange(a1, a2, b1, b2, nrow = 2, ncol = 2) +
  bgcolor("White")
ggsave("/home/timvigers/OneDrive/Vigers/CF/Jordana Hoppe/SSwAB-IT/Dissemination/Figures/fig.png",
  plot = p1, width = 9, height = 6, units = "in"
)
a1 <- plot(euler(d_overall == "Positive"),
  quantities = list(cex = 3),
  main = "Any CF Pathogen"
)
b1 <- plot(euler(d_MSSA == "Positive"),
  quantities = list(cex = 3),
  main = "MSSA"
)
p2 <- ggarrange(a1, b1, nrow = 1, ncol = 2) +
  bgcolor("White")
ggsave("/home/timvigers/OneDrive/Vigers/CF/Jordana Hoppe/SSwAB-IT/Dissemination/Figures/euler_bw.png",
  plot = p2, width = 9, height = 6, units = "in"
)
a1 <- plot(venn(d_overall == "Positive"),
  quantities = list(cex = 3),
  main = "Any CF Pathogen"
)
b1 <- plot(venn(d_MSSA == "Positive"),
  quantities = list(cex = 3),
  main = "MSSA"
)
p3 <- ggarrange(a1, b1, nrow = 1, ncol = 2) +
  bgcolor("White")
ggsave("/home/timvigers/OneDrive/Vigers/CF/Jordana Hoppe/SSwAB-IT/Dissemination/Figures/venn_bw.png",
  plot = p3, width = 9, height = 6, units = "in"
)
```
